r5r: rapid realistic routing on multimodal transport networks with R5 in R

### 2021-01-19 r-package/paper2020/paper2020.Rmd
small paper tweaking and comments removing

<!-- Examples of similar papers -->

<!--  - https://transportfindings.org/article/8416-accessibility-toolbox-for-r-and-arcgis -->

<!--  - https://transportfindings.org/article/6945-dodgr-an-r-package-for-network-flow-aggregation -->

<!--  - https://joss.theoj.org/papers/10.21105/joss.01926 -->

@@

<!-- In the example above we calculated how the estimates of travel-time to arrive at the central bus station vary by place of trip origin.  -->

The plot below shows how the travel times to arrive at the central bus station from several origin points vary within the time window (percentiles 20th, 40th, 60th, 80th, 99th), reflecting that these travel times are more uncertain when leaving from some places than others. While there is little to no uncertainty when departing from places that are very close (walking distance) to the central bus station, travel times from farther away places are more affected by variations departure time and service frequency levels.

@@

<!-- If the destination points cover the entire study area, the output can easily be used to build ishochrone-like visualizations.  -->

@@

```{=html}
<!-- old isochrone code
# ```{r}
# cutoffs <- seq(0, 120, 20)
# 
# # select the travel time matrix departing from a given origin
# central_bus_stn <- points[291,]
# ttm_iso <- ttm[fromId %in% central_bus_stn$id ] 
# 
# # aggregate travel-times
# ttm_iso[, isochrones := cut(x=travel_time_p099, breaks=cutoffs), by= fromId]
#   
# # join travel-matrix results to points
# ttm_iso[points, on=c('toId' ='id'), `:=`(lon = i.lon, lat = i.lat)]
# 
# ggplot(ttm_iso, aes(x=lon, y=lat, colour = isochrones)) +
#    geom_point(size = 2) +
#    geom_point(data = central_bus_stn, aes(x=lon, y=lat), colour="blue", size = 2) +
#    coord_map() +
#    scale_colour_brewer(palette = "Reds") +
#    facet_wrap(~fromId) +
#    theme_minimal() +
#    theme(axis.title = element_blank(),
#          panel.border = element_rect(fill = NA, colour = "grey40"))
# ```
 -->
```

>>>>

@@

The plot below shows how the travel times to arrive at the central bus station from several origin points vary within the time window (percentiles 20th, 40th, 60th, 80th, 99th), reflecting that these travel times are more uncertain when leaving from some places than others. While there is little to no uncertainty when departing from places that are very close (walking distance) to the central bus station, travel times from places farther away are more affected by departure time variations and service frequency levels.

@@

@@
